### 2014-10-31 fundamentals/qa.tex
commas

Integration tests are any tests that combine multiple elements of the 
\Cyclus interface and test that they work correctly with each other.  By analogy, 
simply because the gears (units) are made correctly does not imply that the 
clock (integration) will run smoothly, run at all, or give the correct time.
In \Cyclus and \Cycamore, integration tests are performed by running sample
simulations and verifying that results are what would be expected ahead of 
time. Pre-canned input files have thus been constructed. Their results 
are inspected and compared via nose \cite{pellerin_nose_2007}, a Python test framework.
Python will run \Cyclus as a subprocess for each integration test. In this
way \Cyclus code units are tested in the full context that they will
executed. This category of testing is especially useful for ensuring that 
major \Cyclus components are functioning as expected.

@@

Regression tests are tests which ensure that significant changes do not 
occur over the course of \Cyclus development. Such a change is called a 
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute fully fledged \Cyclus simulations whose results
are then compared. In this category however the comparison is done against 
the output of the same input file when run with a previous version of \Cyclus, 
typically the last released version.
In some sense, regression tests are `dumb' in that they do 
not care about the contents of a simulation being correct, only whether or not 
it changed. They thus pick up glaring time-sensitive mistakes that may 
not appear elsewhere though they do not purport to make claims about the
quality of the physics modeled. The \Cycamore project is the primary location of
regression tests. This is because the archetypes here are sophisticated enough
to make interesting input files. Only a handful ($<10$) time steps are needed 
for regression testing.

>>>>

Integration tests are any tests that combine multiple elements of the 
\Cyclus interface and test that they work correctly with each other.  By analogy, 
simply because the gears (units) are made correctly does not imply that the 
clock (integration) will run smoothly, run at all, or give the correct time.
In \Cyclus and \Cycamore, integration tests are performed by running sample
simulations and verifying that results are what would be expected ahead of 
time. Pre-canned input files have thus been constructed. Their results 
are inspected and compared via nose \cite{pellerin_nose_2007}, a Python test framework.
Python will run \Cyclus as a subprocess for each integration test. In this
way, \Cyclus code units are tested in the full context that they will
executed. This category of testing is especially useful for ensuring that 
major \Cyclus components are functioning as expected.

@@

Regression tests are tests which ensure that significant changes do not 
occur over the course of \Cyclus development. Such a change is called a 
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute fully fledged \Cyclus simulations whose results
are then compared. In this category, however, the comparison is done against 
the output of the same input file when run with a previous version of \Cyclus, 
typically the last released version.
In some sense, regression tests are `dumb' in that they do 
not care about the contents of a simulation being correct, only whether or not 
it changed. They thus pick up glaring time-sensitive mistakes that may 
not appear elsewhere though they do not purport to make claims about the
quality of the physics modeled. The \Cycamore project is the primary location of
regression tests. This is because the archetypes here are sophisticated enough
to make interesting input files. Only a handful ($<10$) time steps are needed 
for regression testing.
